Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2018-01-22 paper/paper.Rmd
Characteristics tables captions

```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Characteristics recorded for each image.")
```

<!--
\begin{table}[htp]
\label{tab:Scene-Attributes-Table}
\caption{Image descriptions that are associated with the attributes of each image. }
\centering
\begin{tabular}{lp{12cm}} \hline
Attribute & Choices \\\hline
Graphic & Live Image, 2D Graphic \\
Background & Crowd, Court, Logo Wall, Not Applicable \\
Person & Yes, No \\
Shot Angle & Level, Birds Eye, Upward \\
Situation & Match play, Close up, Not player, Crowd, Off court, Transition\\\hline
\end{tabular}
\end{table}
-->

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Characteristics recorded for each  face. Most were easy to assess for each face, with the exception of obscured and head angle.")
```

>>>>

```{r Scene-Attributes-Table, fig.cap ="\\label{tab:Scene-Attributes-Table}"}
knitr::kable(SceneAttributes, format = "latex", longtable=FALSE, booktabs =TRUE, caption = "Characteristics of the scene occuring when the still shot was taken, one option for each category was selected for each image.")
```

@@

```{r Face-Attribute-Tables, results='asis', fig.cap = "\\label{tab:Face-Attribute-Tables}"}
knitr::kable(FaceAttributes, format = "latex", longtable=FALSE, booktabs = TRUE, caption = "Characteristics of the faces captured, one option for each category was selected for each face manually tagged.")
```
